A Dataset of Operator-client Dialogues Aligned with Database Queries for End-to-end Training

### 2016-06-28 paper.tex
further fixes

\vspace{-1.00em}
\subsection{Operator Interface}
\label{sec:operator}
The operator CF worker is asked to politely address the clients needs according to the information stored in the database.
In order to provide the information to clients, the operator uses the simple database interface depicted in~Figure~\ref{fig:operator}:
They filter the restaurants using a full text search over the database.
The~search interface is implemented in Javascript as a simple substring matching over values in the database.
We used such a simple interface because it is easy use for untrained CF workers.
Multiple constrains can be expressed by two substrings separated by a comma.
The content of the database is intentionally hidden if no filter is specified so that a filter has to be used to provide results.
The CF workers are also instructed to explicitly mark the database rows to which they refer in their answer.
Similarly to the client role, the operator does not have to provide all requested information in a single turn.
It is left up to the~worker which information is provided first.

@@

In a~single CF task submission, we let the workers append a~single response to multiple different dialogues, taking on a random role in each of them.
The conversations are typically rather short circa four turns and therefore, full dialogues are collected after few rounds of submissions.
The workers are paid  the same amount of money for every submitted response regardless of whether they play the client or the operator role.

@@

\section{Dataset Properties} \label{sec:props}
\vspace{-0.50em}
We just started to collect our dataset and so far, we have only collected \OP{62} conversations.
The average length of a conversation is \OP{3.8} turns, meaning that the contributors in both roles reply in average circa three times before the conversation is finished\footnote{The first system utterance is automatically generated and for some conversations, the first client reply is also generated automatically, as described in Section~\ref{sec:async}}.
During an average conversation, \OP{2.4} goals are requested and \OP{1.9} answered.
There are two reason why there is more goals requested than answered.
We saw a rare case when the goal was actually answered, but was not left marked as unanswered.
However, much more common case is that the client asks for several goals e.g. phone and address, but he is satisfied if the operator provides just one of the goals e.g. phone. 
% Typically in \OP{65} \% case the conversation is ended by the client.
% As we mention the conversation are short, taking only from \OP{four to six turns} including first turn with greetings.
% \begin{table}
% \begin{center}
% \begin{tabular}{lrr}
% \hline
% Set   & \# Dialogues & \# Turns \\
% \hline
% % Joint  &  todo &  todo \\
% % /a/SSD/oplatek/e2end/log/2016-06-08-17-31-38.400-dstc-INDEP_labels-d0.7-w100-e100/
% % /a/SSD/oplatek/e2end/log/TEST-ORIGINAL-2016-06-08-17-31-38.400dstc-INDEP_labels-d0.7-w100-e100-reward-0.9080-step-0036224
% Train  &   ? & ? \\
% Dev &   ? & ? \\
% Test &   ? & ? \\
% \hline
% \end{tabular}
% \caption{Accuracy on development and test set}
% \vspace{-2em}
% \end{center}
% \label{tab:props}
% \end{table}
During the data collection process we discarded around \OP{35} \% of replies so far because the utterances were of low quality.
Note that we discard only the low-quality utterance; the prefix of the conversation is submitted for finishing the conversation in a next round of CF tasks.
Once we collect enough conversations, we intend to split them into training, development and test set. % (see Table~\ref{tab:props}).

>>>>

\vspace{-1.00em}
\subsection{Operator Interface}
\label{sec:operator}
The operator CF worker is asked to politely address the clients needs according to the information stored in the database.
In order to provide the information to clients, the operator uses the simple database interface depicted in~Figure~\ref{fig:operator}:
They filter the restaurants using a full text search over the database.
The~search interface is implemented in Javascript as a simple substring matching over values in the database.
We used such a simple interface because it is easy use for untrained CF workers.
Multiple constrains can be expressed by two substrings separated by a comma.
The content of the database is intentionally hidden.
If no filter value is specified, the operator does not see content of the database so the filter has to be used to answer clients questions.
The CF workers are also instructed to explicitly mark the database rows to which they refer in their answer.
Similarly to the client role, the operator does not have to provide all requested information in a single turn.
It is left up to the~worker which information is provided first.

@@

In a~single CF task submission, we let the workers append a~single response to multiple different dialogues, taking on a random role in each of them.
The conversations are typically rather short circa four turns and therefore, full dialogues are collected after few rounds of submissions.
The workers are paid  the same amount of money for every submitted response regardless of dialogue history length and whether they play the client or the operator role.

@@

\section{Dataset Properties} \label{sec:props}
\vspace{-0.50em}
We just started to collect our dataset and so far, we have only collected \OP{62} conversations.
The average length of a conversation is \OP{3.8} turns, meaning that the contributors in both roles reply in average circa three times before the conversation is finished\footnote{The first system utterance is automatically generated and for some conversations, the first client reply is also generated automatically, as described in Section~\ref{sec:async}}.
During an average conversation, \OP{2.4} goals are requested and \OP{1.9} answered.
There are two reason why there is more goals requested than answered.
We saw a rare case when the goal was actually answered, but was left marked as unanswered.
However, more common case is that the client asks for several goals e.g. phone and address, but he is satisfied if the operator provides just one of the goals e.g. phone. 
% Typically in \OP{65} \% case the conversation is ended by the client.
% As we mention the conversation are short, taking only from \OP{four to six turns} including first turn with greetings.
% \begin{table}
% \begin{center}
% \begin{tabular}{lrr}
% \hline
% Set   & \# Dialogues & \# Turns \\
% \hline
% % Joint  &  todo &  todo \\
% % /a/SSD/oplatek/e2end/log/2016-06-08-17-31-38.400-dstc-INDEP_labels-d0.7-w100-e100/
% % /a/SSD/oplatek/e2end/log/TEST-ORIGINAL-2016-06-08-17-31-38.400dstc-INDEP_labels-d0.7-w100-e100-reward-0.9080-step-0036224
% Train  &   ? & ? \\
% Dev &   ? & ? \\
% Test &   ? & ? \\
% \hline
% \end{tabular}
% \caption{Accuracy on development and test set}
% \vspace{-2em}
% \end{center}
% \label{tab:props}
% \end{table}

During the data collection process we discarded around \OP{35} \% of replies so far because the utterances were of low quality.
Note that we discard only the low-quality utterance; the prefix of the conversation is submitted for finishing the conversation in a next round of CF tasks.
Once we collect enough conversations, we intend to split them into training, development and test set. % (see Table~\ref{tab:props}).
